
#### A.1
```{r, echo = FALSE}
expr <- function(s) (56*s+56)/(s^2+4*s+8)
x_zero <- c(-1)
y_zero <- c(0)
x_pole <- c(-2,-2)
y_pole <- c(2,-2)
pole_zero_plot(x_zero, y_zero, x_pole, y_pole, 5,expr,5)

```

Vi har:

$$ 
V_{in} = \text{DC} \quad Gain = 7 \quad z_1 = -1 \quad p_1 = -2 + 2 j \quad p_2 = -2 - 2j
$$

Derfor:
$$ H(s) =  K \cdot \frac{s+1}{(s+2+2j)(s+2-2j)} $$

Omskriv til frekvensdomæne:
$$ s = \omega j \qquad  \omega = 0 \; \text{for DC}$$

Hvorfor:
$$H(0) = K \cdot \frac{0+1}{(0+2+2j)(0+2-2j)} = 7 $$
$$H(0) = \frac{K}{(2+2j)(2-2j)} = 7 $$
$$H(0) = \frac{K}{4-4j+4j+4} = 7 $$
$$H(0) = \frac{K}{8} = 7 $$
$$K = 7 \cdot 8 $$
$$K = 56 $$

Dermed:

$$\boxed{ H(s) = \frac{56(s+1)}{(s+2+2j)(s+2-2j)} }$$
 
Bodeplot der viser $|H(s)|$ og $\mathrm{arg}(H(s))$: 

```{r, echo = FALSE}

library("freqr")
bodeplot(fr = c(-3,6),
        n = c(56, 56),
        d = c(0, 1, 4, 8),
#        highlight = 0.5,
        label = "Highlight",
        )
```

#### A.2

```{r, echo = FALSE}
expr <- function(s) (18)/((s+3)*(s+2))
x_zero <- c()
y_zero <- c()
x_pole <- c(-2,-3)
y_pole <- c(0,0)
pole_zero_plot(x_zero, y_zero, x_pole, y_pole, 4,expr,5)

```
Vi har:

$$
 V_{in} = \text{DC} \quad Gain = 3 \quad p_1 = -3 \quad p_2 = -2
$$

Derfor:

$$
H(s) = K \cdot \frac{1}{(s+3)(s+2)}
$$

Omskriv til frekvensdomæne:
$$ s = \omega j \qquad  \omega = 0 \; \text{for DC}$$

Hvorfor:
$$ K \frac{1}{(0+3)(0+2)} = 3 $$
$$\frac{K}{6} = 3 $$
$$K = 18 $$

Dermed:

$$
\boxed{ H(s) = \frac{18}{(s+3)(s+2)}}
$$

```{r, echo = FALSE }
library("freqr")
bodeplot(fr = c(-3,6),
        n = c(0, 18),
        d = c(0, 1, 5, 6),
#        highlight = 0.5,
        label = "Highlight",
        )
```


#### A.3

```{r, echo = FALSE}
expr <- function(s) (-156)/(s^5+13*s^4+60*s^3+120*s^2+124*s+52)
x_zero <- c()
y_zero <- c()
x_pole <- c(-5,-5,-1,-1,-1)
y_pole <- c(1,-1,1,-1,-0)
pole_zero_plot(x_zero, y_zero, x_pole, y_pole, 6,expr)
```

Vi har :

$$
 V_{in} = \text{DC} \quad Gain = -3
$$

$$  p_1 = -5+j \quad p_2 = -5-j \quad p_3 = -1+j \quad p_4 = -1-j  \quad p_5 = -1  $$

Dermed:

$$
 H(s) = \frac{K}{(s+5+j)(s+5-j)(s+1+j)(s+1-j)(s+1)}
$$

Omskriv til frekvensdomæne:
$$ s = \omega j \qquad  \omega = 0 \; \text{for DC}$$

$$ H(0) = \frac{K}{(0+5+j)(0+5-j)(0+1+j)(0+1-j)(0+1)} = -3$$
$$ H(0) = \frac{K}{(5+j)(5-j)(1+j)(1-j) \cdot 1} = -3 $$
$$ H(0) = \frac{K}{52}  = -3 $$
$$ K = -3 \cdot 52 $$
$$ K = -156 $$

Derfor:

$$
\boxed{
 H(s) = \frac{-156}{(s+5+j)(s+5-j)(s+1+j)(s+1-j)(s+1)}
}
$$

$$
\boxed{
 H(s) = \frac{-156}{s^5+13s^4+60s^3+120s^2+124s+52}
}
$$

```{r,echo=FALSE}
bodeplot(fr = c(-3,6),
        n = c(0, -156),
        d = c(0, 1, 13, 60, 120, 124, 52),
#        highlight = 0.5,
        label = "Highlight",
        )

```


#### A.4

```{r, echo = FALSE}
expr <- function(s) (-10*s^2+10*s+20)/(s^2+7*s+10)
x_zero <- c(-1,2)
y_zero <- c(0,0)
x_pole <- c(-5,-2)
y_pole <- c(0,0)
pole_zero_plot(x_zero, y_zero, x_pole, y_pole, 6,expr)
```

Vi har :

$$
 V_{in} = \text{DC} \quad Gain = 2
$$

$$
z_1 = -1 \quad z_2 = 2 \quad p_1 = -5 \quad p_2 = -2
$$

Derfor:

$$
H(s) = K \frac{(s+1)(s-2)}{(s+5)(s+2)}
$$

Omskriv til frekvensdomæne:
$$ s = \omega j \qquad  \omega = 0 \; \text{for DC}$$

$$
H(s) = K \frac{(0+1)(0-2)}{(0+5)(0+2)} = 2
$$

$$
\frac{K}{10} = -1
$$

$$
K = -10
$$

Derfor:

$$
H(s) = -10 \frac{(s+1)(s-2)}{(s+5)(s+2)}
$$

```{r, echo = FALSE }
library("freqr")
bodeplot(fr = c(-3,6),
        n = c(-10,10,20),
        d = c(1,7,10),
#        highlight = 0.5,
        label = "Highlight",
        )

```

#### A.5
```{r, echo = FALSE}

expr <- function(s) (26*(s+1))/(s^2+10*s+26)
x_zero <- c(-1)
y_zero <- c(0)
x_pole <- c(-5,-5)
y_pole <- c(1,-1)
pole_zero_plot(x_zero, y_zero, x_pole, y_pole, 6,expr)
```

Vi har :

$$
 V_{in} = \text{DC} \quad Gain = 1
$$

$$
z_1 = -1 \quad z_2 = 2 \quad p_1 = -5+j \quad p_2 = -5-j
$$

Derfor:

$$
H(s) = K \frac{(s+1)}{(s+5-j)(s+5+j)}
$$

Omskriv til frekvensdomæne:
$$ s = \omega j \qquad  \omega = 0 \; \text{for DC}$$

$$
H(s) = K \frac{(1)}{(5-j)(5+j)} = 1
$$

$$
K = 26
$$

Derfor:

$$
H(s) = 26 \frac{(s+1)}{(s+5-j)(s+5+j)}
$$

```{r, echo = FALSE }
library("freqr")

bodeplot(fr = c(-3,6),
        n = c(0,26),
        d = c(1,10,26),
#        highlight = 0.5,
        label = "Highlight",
        )
```


#### A.6

```{r, echo = FALSE}
expr <- function(s) 14/(s^3+3*s^2+2*s)
x_zero <- c()
y_zero <- c()
x_pole <- c(-2,-1,0)
y_pole <- rep(0,3)
pole_zero_plot(x_zero, y_zero, x_pole, y_pole, 6,expr)
```

Vi har :

$$
H(0) = 7
$$

$$
p_1 = -2 \quad p_2 = -1 \quad p_3 = 0
$$

Derfor:

$$
$$

Givet:
$$ \lim_{s \to 0} H(s) = 7$$
$$ \lim_{s \to 0} K \frac{1}{s^3+3s^2+2s} = 7$$
$$ K = 14$$
Derfor:
$$ H(s) = \frac{14}{(s+2)(s+1)\cdot s} $$

```{r, echo = FALSE }
library("freqr")
bodeplot(fr = c(-3,6),
        n = c(0,14),
        d = c(1,3,2),
#        highlight = 0.5,
        label = "Highlight",
        )
```


#### A.7

```{r, echo = FALSE}

expr <- function(s) -(8/5)*((s^2+3*s-10)/(s^3+4*s^2+8*s))
x_zero <- c(-5,2)
y_zero <- c(0,0)
x_pole <- c(0,-2,-2)
y_pole <- c(0,2,-2)
pole_zero_plot(x_zero, y_zero, x_pole, y_pole, 6,expr)
```

Vi har :

$$
H(0) = 2
$$

$$
z_0 = -5 \quad z_1 = 2 \quad p_1 = 0 \quad p_2 = -2+2j \quad p_3 = -2-2j
$$

Derfor:

$$
H(s) = K \cdot \frac{(s+5)(s-2)}{s(s+2-2j)(s+2+2j)}
$$

Med slutværdien indsat:

$$
\lim_{s \to 0} s H(s) = 2
$$

$$
\lim_{s \to 0} s  K \cdot \frac{(s+5)(s-2)}{s(s+2-2j)(s+2+2j)} = 2
$$

Dette giver:

$$ K = \frac{-8}{5} $$

Hvorfor:

$$
H(s) = \frac{-8}{5} \cdot \frac{(s+5)(s-2)}{s(s+2-2j)(s+2+2j)}
$$
